Argennon: A Scalable Cloud Based Smart Contract Platform

### 2022-08-06 tex/sections/intro.tex
Fix some readability issues in Chapter 1
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

To overcome these difficulties, Argennon uses a Hybrid Proof of Stake consensus protocol, which is
capable of combining the benefits of a centralized and a decentralized system. A small committee of
delegates is democratically elected
by the Argennon users and is responsible for minting new blocks of the blockchain. Each
minted block is required to get approved by its corresponding validator committee. Validator committees are very
large sets of validators including at least three percent of the total stake of the system. A block is approved if it
gets approval votes from at least \(2/3\) of the total stake of its validator committee.

Every block of the Argennon blockchain needs a certificate from both the committee of delegates and
the committee of validators. A block is considered final after its \textbf{next} block receives \textbf{both} of
its certificates. The Argennon protocol ensures that as long as more than half of the total stake of validators is
controlled by honest users, the probability of discarding a final block is near zero even if all the delegates are
malicious.

Block generation is centralized in Argennon. This brings some interesting features to the Argennon platform, such as off
chain fee payment, optimistic instant transaction confirmation and runoff protection. However, centralized
block generation also increases the possibility of transaction censorship. This problem is addressed by a special
High Priority Transaction (HPT) protocol in Argennon.

@@

Argennon applications (i.e smart contracts) are stored in a high level text based language on the Argennon
blockchain. This language is intended for preserving the
high level information of the application logic to facilitate platform specific compiler optimization at a host
machine. This enables delegates to compile and optimize Argennon applications for their specific hardware platforms
and execute applications efficiently.

>>>>

To overcome these difficulties, Argennon uses a Hybrid Proof of Stake consensus protocol, which is
capable of combining the benefits of a centralized and a decentralized system. A small committee of
delegates is democratically elected
by the Argennon users and is responsible for minting new blocks of the blockchain. Each
minted block is required to get approved by its corresponding validator committee. Validator committees are very
large sets of validators including at least three percent of the total stake of the system. A block is approved if it
takes approval votes from at least \(2/3\) of the total stake of its validator committee.

Every block of the Argennon blockchain needs a certificate from both the committee of delegates and
the committee of validators. A block is considered final after its \textbf{next} block gets \textbf{both} of
its certificates. The Argennon protocol ensures that as long as more than half of the total stake of validators is
controlled by honest users, the probability of discarding a final block is near zero even if all the delegates are
malicious.

Centralized block generation brings some interesting features to the Argennon platform, such as off
chain fee payment, optimistic instant transaction confirmation and runoff protection. However, it also increases
the possibility of transaction censorship. In Argennon, this problem is addressed by a special
High Priority Transaction (HPT) protocol.

@@

Argennon applications (i.e smart contracts) are stored in a high level text based language on the blockchain. This
language is intended for preserving the
high level information of the application logic to facilitate platform specific compiler optimization at a host
machine. This enables delegates to compile and optimize Argennon applications for their specific hardware platforms
and execute applications efficiently.
